\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-15 manuscript.Rmd
packrat updates

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
r_refs("references.bib")
```

>>>>

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
install.packages("plyr")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
r_refs("references.bib")
```
